\begin{thebibliography}{20}

\bibitem{mikal13}
  Jude P. Mikal, Ronald E. Rice, Audrey Abeyta, Jenica DeVilbiss.
  2013.
  \emph{Transition, stress and computer-mediated social support}
  Computers in Human Behavior 29.5 (2013): A40-A53.

\bibitem{rains09}
  Rains, Stephen A., and Valerie Young.
  \emph{A Meta-Analysis of Research on Formal Computer-Mediated Support Groups: Examining Group Characteristics and Health Outcomes.}
  Human Communication Research 35.3 (2009): 309-336

\bibitem{shor13}
  Shor, Eran, David J. Roelfs, and Tamar Yogev.
  \emph{The strength of family ties: A meta-analysis and meta-regression of self-reported social support and mortality.}
  Social Networks 35.4 (2013): 626-638.

\bibitem{lehman86}
  Lehman, Darrin R., John H. Ellard, and Camille B. Wortman.
  \emph{Social support for the bereaved: Recipients' and providers' perspectives on what is helpful.}
  Journal of Consulting and Clinical Psychology 54.4 (1986): 438.

\bibitem{vachon88}
  Vachon, Mary LS, and Stanley K. Stylianos.
  \emph{The role of social support in bereavement.}
  Journal of Social Issues 44.3 (1988): 175-190.

\bibitem{mm11a}
  Massimi, M. and Baecker, R.M.
  \emph{Dealing with death in design: Developing systems for the bereaved.}
  Proc. ACM SIGCHI 2011, 1001-1010

\bibitem{mm10}
  Michael Massimi and Ronald M. Baecker.
  2010.
  \emph{A death in the family: opportunities for designing technologies for the
  bereaved.}
  In Proceedings of the SIGCHI Conference on Human Factors in Computing
  Systems (CHI '10).
  ACM, New York, NY, USA, 1821-1830. 

\bibitem{mm13}
  Michael Massimi.
  2013.
  \emph{Exploring remembrance and social support behavior in an online
  bereavement support group.}
  In Proceedings of the 2013 conference on Computer supported cooperative
  work (CSCW '13). ACM, New York, NY, USA, 1169-1180. 

\bibitem{brubaker11}
  Jed R. Brubaker and Gillian R. Hayes.
  2011.
  \emph{"We will never forget you [online]"}
  In Proceedings of the ACM 2011 conference on Computer supported cooperative
  work
  (CSCW '11). ACM, New York, NY, USA, 123-132. 

\bibitem{neustaedter12}
  Carman Neustaedter, Steve Harrison, and Abigail Sellen.
  2012.
  \emph{Connecting Families: The Impact of New Communication Technologies on
  Domestic Life.}
  Springer Publishing Company, Incorporated.

\bibitem{neustaedter06}
  Carman Neustaedter, Kathryn Elliot, and Saul Greenberg.
  2006.
  \emph{Interpersonal awareness in the domestic realm.}
  In Proceedings of the 18th Australia conference on Computer-Human Interaction:
  Design: Activities, Artefacts and Environments (OZCHI '06),
  Jesper Kjeldskov and Jeni Paay (Eds.). ACM, New York, NY, USA, 15-22.

\bibitem{markopoulos04}
  Panos Markopoulos, Natalia Romero, Joy van Baren, Wijnand IJsselsteijn,
  Boris de Ruyter, and Babak Farshchian.
  2004.
  \emph{Keeping in touch with the family: home and away with the ASTRA awareness
  system.}
  In CHI '04 Extended Abstracts on Human Factors in Computing Systems.
  ACM, New York, NY, USA, 1351-1354.

\bibitem{pollack11}
  John P. Pollak, Phil Adams, and Geri Gay.
  2011.
  \emph{PAM: a photographic affect meter for frequent, in situ measurement of
  affect.}
  In Proceedings of the SIGCHI Conference on Human Factors in Computing Systems
  (CHI '11). ACM, New York, NY, USA, 725-734. 

\bibitem{mm11b}
  Michael Massimi.
  2011.
  \emph{Technology and the human lifespan: learning from the bereaved.}
  interactions 18, 3 (May 2011), 26-29.

\bibitem{hassenzhal12}
  Marc Hassenzhal, Stephanie Heidecker, Kai Eckoldt, and Satah Deifenbach.
  2012.
  \emph{All You Need is Love: Current Strategies of Mediating Intimate
  Relationships through Technology}
  ACM Transactions on Computer-Human Interaction, Vol. 19, No. 4, Article 30

\bibitem{vetere05}
  Frank Vetere, Martin R. Gibbs, Jesper Kjedskov.
  2005.
  \emph{Mediating Intimacy: Designing Technologies to Support
  Strong-Tie Relationships}
  CHI 2005, April 2–7, 2005, Portland, Oregon, USA.

\bibitem{lottridge09}
  Danielle Lottridge, Nicolas MAsson, Wendy Mackay
  2009.
  \emph{Sharing Empty Moments: Design for Remote Couples}
  CHI 2009, April 4–9, 2009, Boston, MA, USA.

\bibitem{octavia07}
  Johanna Renny Octavia, Elise van den Hoven, Hans De Mondt.
  2007
  \emph{Overcoming the Distance Between Friends}
  HCI 2007, 3-7 September 2007, Lancaster University, UK.

\bibitem{brush08}
  A.H. Bernhein Brush, Kori M Inkpen, Kimberly Tee.
  2008.
  \emph{SPARCS: Exploring Sharing Suggestions
  to Enhance Family Connectedness}
  CSCW’08, November 8–12, 2008, San Diego, California, USA.

\bibitem{skeels10}
  Meredith M. Skeels, Kenton T. Unruh, Christopher Powell, Wanda Pratt.
  2010.
  \emph{Catalyzing Social Support for Breast Cancer Patients}
  CHI 2010, April 10–15, 2010, Atlanta, Georgia, USA

\end{thebibliography}
